### 2018-11-15 Sections/cryptowars.tex
braket
CV
CV QKD update

\subsubsection{Continuous-variable protocols}\index{Continuous-variables!QKD}

@@

Note that this protocol provides information-theoretic security\index{Information-theoretic security}, as per BB84\index{BB84 protocol}, despite the fact that coherent states are non-orthogonal, forming an over-complete basis in phase-space.

Conceptually, the operation of the CV QKD protocol is virtually identical to photonic BB84, differing only in that now the different choices of encodings correspond to phase-space transformations. Like BB84, if Eve were to perform an intercept-resend attack\index{Intercept-resend attacks} she would probabilistically re-encode in the wrong quadrature, thereby revealing herself to Alice and Bob, who could then terminate.

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function CVQKD():
\begin{enumerate}
\item Alice chooses two Gaussian-distributed random numbers with mean zero,
\begin{align}
x_A &= \mathcal{N}(0,V_\mathrm{mod}),\nonumber \\
p_A &= \mathcal{N}(0,V_\mathrm{mod}),
\end{align}
where $V_\mathrm{mod}$ is the modulation variance\index{Modulation variance}.
\item Alice prepares the coherent state,
\begin{align}
\ket\alpha = \ket{x_A+ip_A}.	
\end{align}
\item Alice transmits $\ket\alpha$ to Bob.
\item Bob randomly measures either $\hat{x}$ or $\hat{p}$ using homodyne detection.
\item Alice and Bob use classical communication to determine for which transmissions their preparation and measurement were consistent \comment{I don't get this, Alice is deterministically encoding x+ip, where's the randomness in the choice of basis? Are we adding a randomised phase that puts us into a diagonal basis sometimes, or something like that}
\item \comment{Complete the rest of this}
\item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{CV QKD protocol using coherent states, encoded in the quadrature basis.}\label{alg:cv_qkd}
\end{table}

\comment{To do.}

@@

Importantly, unlike classical cryptographic protocols, QKD makes no assumptions about the computational complexity of inverting encoding algorithms or trapdoor functions. The protocols are information-theoretically secure\index{Information-theoretic security}, and therefore no physically realisable computer, even a quantum computer, can compromise them. Thus, usual cryptanalytic techniques, like linear and differential cryptanalysis \cite{bib:Schneier96}\index{Linear cryptanalysis}\index{Differential cryptanalysis}, or the ability to factor large numbers\index{Integer factorisation}, that are employed to attack other encryption protocols, do not compromise QKD.

@@

To characterise the security of the scheme, we first note that in the absence of knowing the key or message, and assuming all $j$ and $k$ are equally likely, Eve observes the mixed state,
\begin{align}
\hat\rho_\mathrm{enc} &= \frac{1}{2^{m+n}} \sum_{j,k} \hat{U}_k\ket{j}\bra{j}\hat{U}^\dag_k \nonumber\\
&= \frac{1}{2^{m+n}} \sum_{j,k} \ket{j}_k\bra{j}_k.
\end{align}
The security can now be quantified in terms of the accessible information\footnote{The accessible information is the maximum of the mutual information between Alice's input states and measurements performed on the encoded state by Eve.}\index{Accessible information} between this state and the plaintext state, which can be upper-bounded as,
\begin{align}
	I_c \leq n + \frac{1}{2^m}\max_{\ket\phi}\sum_{j,k} |\langle \phi|j\rangle_k|^2 \log |\langle \phi|j\rangle_k|^2.
\end{align}
It was shown that this quantity can be made arbitrarily small with key-size scaling as,
\begin{align}
m=O(\log n),
\end{align}
which represents very frugal requirements in key-size versus message length. They further showed that the scheme can be made robust against noise and loss.

>>>>

\subsubsection{Continuous-variable protocols}\index{Continuous-variables!Quantum key distribution}\label{sec:CV_QKD}

@@

Note that this protocol provides information-theoretic security\index{Information-theoretic security}, as per BB84\index{BB84 protocol}, despite the fact that coherent states are non-orthogonal, forming an over-complete basis in phase-space\index{Phase-space}.

Conceptually, the operation of the CV QKD protocol is virtually identical to photonic BB84, differing only in that now the different choices of encodings correspond to phase-space transformations. Like BB84, if Eve were to perform an intercept-resend attack\index{Intercept-resend attacks} she would probabilistically re-encode in the wrong quadrature\index{Quadratures}, thereby revealing herself to Alice and Bob, who could then terminate and start over.

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function CV\_QKD():
\begin{enumerate}
\item Alice chooses two Gaussian-distributed random numbers with mean zero,
\begin{align}
x_A &= \mathcal{N}(0,V_\mathrm{mod}),\nonumber \\
p_A &= \mathcal{N}(0,V_\mathrm{mod}),
\end{align}
where $V_\mathrm{mod}$ is the modulation variance\index{Modulation variance}.
\item Alice prepares the coherent state,
\begin{align}
\ket\alpha = \ket{x_A+ip_A}.	
\end{align}
\item Alice transmits $\ket\alpha$ to Bob.
\item Bob randomly measures either $\hat{x}$ or $\hat{p}$ using homodyne detection\index{Homodyne detection}.
\item Alice and Bob use classical communication to determine for which transmissions their preparation and measurement were consistent.
\item The remainder of the protocol proceeds as per BB84.
\item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{CV QKD protocol using coherent states, encoded in the quadrature basis.}\label{alg:cv_qkd}
\end{table}

@@

Importantly, unlike classical cryptographic protocols, QKD makes no assumptions about the computational complexity of inverting encoding algorithms or trapdoor functions\index{Trapdoor functions}. The protocols are information-theoretically secure\index{Information-theoretic security}, and therefore no physically realisable computer, even a quantum computer, can compromise them. Thus, usual cryptanalytic techniques, like linear and differential cryptanalysis \cite{bib:Schneier96}\index{Linear cryptanalysis}\index{Differential cryptanalysis}, or the ability to factor large numbers\index{Integer factorisation}, that are employed to attack other encryption protocols, do not compromise QKD.

@@

To characterise the security of the scheme, we first note that in the absence of knowing the key or message, and assuming all $j$ and $k$ are equally likely, Eve observes the mixed state,
\begin{align}
\hat\rho_\mathrm{enc} &= \frac{1}{2^{m+n}} \sum_{j,k} \hat{U}_k\ket{j}\bra{j}\hat{U}^\dag_k \nonumber\\
&= \frac{1}{2^{m+n}} \sum_{j,k} \ket{j}_k\bra{j}_k.
\end{align}
The security can now be quantified in terms of the accessible information\footnote{The accessible information is the maximum of the mutual information between Alice's input states and measurements performed on the encoded state by Eve.}\index{Accessible information} between this state and the plaintext state, which can be upper-bounded as,
\begin{align}
	I_c \leq n + \frac{1}{2^m}\max_{\ket\phi}\sum_{j,k} |\braket{ \phi|j}_k|^2 \log |\braket{ \phi|j}_k|^2.
\end{align}
It was shown that this quantity can be made arbitrarily small with key-size scaling as,
\begin{align}
m=O(\log n),
\end{align}
which represents very frugal requirements in key-size versus message length. They further showed that the scheme can be made robust against noise and loss.

### 2018-11-15 Sections/optical_encoding_of_quantum_information.tex
CV QKD update

Another type of CV state, which can in fact encode quantum information, is superpositions of coherent states (colloquially known as `cat' states), with the encoding \cite{???},
\begin{align}
\ket{0} &\equiv \frac{1}{\sqrt{2(1+e^{-2|\alpha|^2})}} (\ket{\alpha}+\ket{-\alpha}) \nonumber \\
&= \ket{\mathrm{cat}_+(\alpha)},\nonumber \\
\ket{1} &\equiv \frac{1}{\sqrt{2(1-e^{-2|\alpha|^2})}}(\ket{\alpha}-\ket{-\alpha}) \nonumber \\
&= \ket{\mathrm{cat}_-(\alpha)}.
\end{align}
These two basis states contain strictly even or odd photon-number terms respectively (i.e they have well-defined parity), implying that, unlike coherent states, they are always orthogonal, regardless of amplitude,
\begin{align}
\braket{\mathrm{cat}_+(\alpha)|\mathrm{cat}_-(\alpha)} = 0 \,\,\forall\,\alpha,
\end{align}
making them directly appropriate for qubit encoding, even for weak coherent amplitudes.

@@

In the same way that information can be encoded using the displacement operator, in the form of coherent states, we can encode information via the squeezing operator\index{Squeezing operator},
\begin{align}\label{eq:sq_op}
\hat{S}(\xi) = \exp\left[ \frac{1}{2}(\xi^*\hat{a}^2 - \xi{\hat{a}^{\dag 2}})\right],
\end{align}
where \mbox{$\xi  = r e^{i \varphi}$}, $r$ is known as the squeezing parameter\index{Squeezing parameter}, which will determine the magnitude of the squeezing and \mbox{$\varphi \in [0, 2\pi]$} denotes that axis along which the squeezing is taking place.

Graphically, in terms of their phase-space visualisation, squeezing implements dilations about a given axis. Strongly squeezing the vacuum state along the $\hat{x}$ or $\hat{p}$ directions yields two states that are approximately orthogonal for large squeezing amplitudes, as shown in Fig.~\ref{fig:squeezed_state_encoding}. Thus, with sufficient squeezing they can be used as a basis for approximating a qubit. This encoding can be exploited for full universal quantum computing, to be discussed in Sec.~\ref{sec:CV_QC}.

>>>>

Another type of CV state, which can in fact encode quantum information, is superpositions of coherent states (colloquially known as `cat' states), with the encoding \cite{???},
\begin{align}
\ket{0} &\equiv \frac{1}{\sqrt{2(1+e^{-2|\alpha|^2})}} (\ket{\alpha}+\ket{-\alpha}) \nonumber \\
&= \ket{\mathrm{cat}_+(\alpha)},\nonumber \\
\ket{1} &\equiv \frac{1}{\sqrt{2(1-e^{-2|\alpha|^2})}}(\ket{\alpha}-\ket{-\alpha}) \nonumber \\
&= \ket{\mathrm{cat}_-(\alpha)}.
\end{align}
These two basis states contain strictly even or odd photon-number terms respectively (i.e they have well-defined parity\index{Parity}), implying that, unlike coherent states, they are always orthogonal, regardless of amplitude,
\begin{align}
\braket{\mathrm{cat}_+(\alpha)|\mathrm{cat}_-(\alpha)} = 0 \,\,\forall\,\alpha,
\end{align}
making them directly appropriate for qubit encoding, even for weak coherent amplitudes.

@@

In the same way that information can be encoded using the displacement operator via coherent states, we can encode information via the single-mode squeezing operator\index{Squeezing operator},
\begin{align}\label{eq:sq_op}
\hat{S}(\xi) = \exp\left[ \frac{1}{2}(\xi^*\hat{a}^2 - \xi{\hat{a}^{\dag 2}})\right],
\end{align}
where \mbox{$\xi  = r e^{i \varphi}\in \mathbb{C}$}, $r$ is known as the squeezing parameter\index{Squeezing parameter}, which will determine the magnitude of the squeezing and \mbox{$\varphi \in [0, 2\pi]$} denotes that axis along which the squeezing is taking place.

Graphically, in terms of their phase-space visualisation, squeezing implements dilations about a given axis. Strongly squeezing the vacuum state along the $\hat{x}$ or $\hat{p}$ directions yields two states that are approximately orthogonal for large squeezing amplitudes, as shown in Fig.~\ref{fig:squeezed_state_encoding}. Thus, with sufficient squeezing they can be used as a basis for \textit{approximating} a qubit. This encoding can be exploited for full universal quantum computing, to be discussed in Sec.~\ref{sec:CV_QC}.

### 2018-11-15 Sections/physical_architectures_for_quantum_computing.tex
minor
CV QKD update

As discussed in Sec.~\ref{sec:squeezed_enc}, position and momentum eigenstates are orthogonal and may therefore be employed to encode a single qubit. However, these eigenstates have infinite energy. That is, they are infinitely squeezed in phase-space\index{Infinite squeezing}. But position and momentum eigenstates can be closely approximated using finite, but strong squeezing. The squeezed states\index{Squeezed states} in the two quadratures will now no longer be orthogonal, but will have a small overlap that asymptotes to zero as squeezing is increased. Thus, squeezed states can be used to approximate qubits using non-orthogonal basis states. Squeezed states may be prepared directly using a spontaneous parametric down-conversion (SPDC)\index{Spontaneous parametric down-conversion (SPDC)} process (Sec.~\ref{sec:single_phot_src}) \cite{bib:PhysRevLett.75.4337, bib:o2009photonic}. CV encoding using squeezed states is illustrated in phase-space in Fig.~\ref{fig:squeezed_state_encoding}.

Mathematically, there are two operators of interest, the single- and two-mode squeezing operators\index{Squeezing operators},
\begin{align}\label{eq:sq_op}
\hat{S}_\mathrm{single}(\xi) &= \exp\left[ \frac{1}{2}(\xi^*\hat{a}^2 - \xi{\hat{a}^{\dag 2}})\right],\nonumber\\
\hat{S}_\mathrm{two}(\xi) &= \exp\left[ \xi(\hat{a}_1^\dag\hat{a}_2^\dag + \hat{a}_1\hat{a}_2) \right].
\end{align}
Both of these may be implemented physically using non-linear crystals\index{Non-linear crystals} with second order non-linearities\index{Second order non-linearities}, readily available in present-day labs.

@@

A phase-shifter\index{Phase-shifters}, implementing the unitary operation,
\begin{align}
\hat{R}(\theta) = e^{i\theta \hat{n}},
\end{align}
where \mbox{$\hat{n}=\hat a^\dag \hat a$} is the photon-number operator\index{Photon-number operator}, rotates a state in phase-space by angle $\theta$, implementing the transformation between the position and momentum operators,
\begin{align}
\begin{pmatrix}
\hat x_{\theta}\\
\hat p_{\theta}
\end{pmatrix}
=
\begin{pmatrix}\cos\theta & \sin\theta \\
-\sin\theta & \cos\theta
\end{pmatrix}
\begin{pmatrix}
\hat x\\
\hat p
\end{pmatrix}.
\end{align}
It is evident upon inspection that this can be thought of as a single-qubit rotation in the position/momentum basis.

@@

In the squeezed state basis one can prepare Bell pairs in an analogous manner to doing so using single-photon encoding. Namely, mixing two orthogonally squeezed states (squeezed and anti-squeezed) on a 50:50 beamsplitter generates Bell pairtype entanglement. This is shown in Fig.~\ref{fig:CV_bell_pair}.

@@

Measurement of CV states may be performed using homodyne detection\index{Homodyne detection} (Sec.~\ref{sec:homodyne}), which performs a projection along an arbitrary axis in phase-space, allowing $\hat{x}$ and $\hat{p}$, or any linear combination of the two, to be directly sampled (i.e we can access the observables $\hat{x}_\theta$ and $\hat{p}_\theta$ for any $\theta$).

Using a 50:50 beamsplitter to implement the reverse of Bell pair preparation, one can construct a Bell analyser for performing projections in the Bell basis\index{Bell measurements}.

@@

The logical generalisation of the CZ gate is,
\begin{align}
\hat{U}_\mathrm{CZ} = e^{\frac{i}{2} \hat x_1 \hat x_2},
\end{align}
which transforms two-mode quadrature eigenstates as,
\begin{align}
\hat{U}_\mathrm{CZ} \ket{s}_1 \ket{t}_2 = e^{\frac{i}{2} s_1 t_2} \ket{s}_1\ket{t}_2.
\end{align}
Intuitively, it's evident upon inspection of the form of the generalised CZ gate that it leaves logical basis state amplitudes unchanged, but adds state-dependent phases to basis states. Qualitatively, this is exactly what a regular CZ gate does in the space of two qubits, except that the basis is discrete rather than continuous.

@@

\begin{figure}[!htbp]
	\begin{align}
		\Qcircuit @C=.7em @R=.4em @! {
		\lstick{\ket{\psi}} & \ctrl{1} & \qw & \meter & \hat{U}^\dag\hat{p}\hat{U} = m \\
		\lstick{\ket{0}_p} & \ctrl{0} & \gate{F} & \gate{X(m)} \cwx & \rstick{\hat{U}\ket\psi} \qw \\
		} \nonumber
	\end{align}
	\captionspacefig \caption{The single-mode teleporter using CV state encoding, structurally identical to an ordinary single-qubit teleporter, just substituting the operations with their respective CV generalisations. The circuit teleports the input state $\ket\psi$ from the first mode to the second mode, accumulating the action of the single-mode gate $\hat{U}$ applied to the first mode prior to measurement.} \label{fig:CV_teleporter}\index{Continuous variables!Teleporter}
\end{figure}

Having demonstrated an equivalent single-mode teleporter, we have all we need to construct arbitrary measurement-based quantum computations using the generalised CZ gates as the primitive entangling operation for preparation of the substrate graph state.

@@

Having demonstrated fault-tolerance, it can be concluded that CV optical quantum computation is possible, and scalable with efficient error correction overheads.

>>>>

As discussed in Sec.~\ref{sec:squeezed_enc}, position and momentum eigenstates are orthogonal and may therefore be employed to encode a single qubit. However, these eigenstates have infinite energy. That is, they are infinitely squeezed in phase-space\index{Infinite squeezing}. But position and momentum eigenstates can be closely approximated using finite, but strong squeezing, where there is a direct tradeoff between energy and the quality of the qubit approximation. The squeezed states\index{Squeezed states} in the two quadratures\index{Quadratures} will now no longer be orthogonal, but will have a small overlap that asymptotes to zero as squeezing is increased. Thus, squeezed states can be used to approximate qubits using non-orthogonal basis states. Squeezed states may be prepared directly using a spontaneous parametric down-conversion (SPDC)\index{Spontaneous parametric down-conversion (SPDC)} process (Sec.~\ref{sec:single_phot_src}) \cite{bib:PhysRevLett.75.4337, bib:o2009photonic}. CV encoding using squeezed states is illustrated in phase-space in Fig.~\ref{fig:squeezed_state_encoding}.

Mathematically, there are two operators of interest, the single- and two-mode squeezing operators\index{Squeezing operators},
\begin{align}\label{eq:sq_op}
\hat{S}_\mathrm{single}(\xi) &= \exp\left[ \frac{1}{2}(\xi^*\hat{a}^2 - \xi{\hat{a}^{\dag 2}})\right],\nonumber\\
\hat{S}_\mathrm{two}(\xi) &= \exp\left[ \xi\hat{a}_1^\dag\hat{a}_2^\dag + \xi^*\hat{a}_1\hat{a}_2 \right],
\end{align}
where \mbox{$\xi\in \mathbb{C}$} is the squeezing parameter. Both of these may be implemented physically using non-linear crystals\index{Non-linear crystals} with second order non-linearities\index{Second order non-linearities}, readily available in present-day labs.

@@

A phase-shifter\index{Phase-shifters}, implementing the unitary operation,
\begin{align}
\hat{R}(\theta) = e^{i\theta \hat{n}},
\end{align}
where \mbox{$\hat{n}=\hat a^\dag \hat a$} is the photon-number operator\index{Photon-number operator}, rotates a state in phase-space by angle $\theta$ about the origin, implementing the transformation between the position and momentum operators,
\begin{align}\label{eq:xp_theta}
\begin{pmatrix}
\hat x_{\theta}\\
\hat p_{\theta}
\end{pmatrix}
=
\begin{pmatrix}\cos\theta & \sin\theta \\
-\sin\theta & \cos\theta
\end{pmatrix}
\begin{pmatrix}
\hat x\\
\hat p
\end{pmatrix}.
\end{align}
It is evident upon inspection that this can be thought of as a single-qubit rotation in the position/momentum basis.

@@

In the squeezed state basis one can prepare Bell pairs in an analogous manner to doing so using single-photon encoding. Namely, mixing two orthogonally squeezed states (squeezed and anti-squeezed) on a 50:50 beamsplitter generates Bell-type entanglement. This is shown in Fig.~\ref{fig:CV_bell_pair}.

@@

Measurement of CV states may be performed using homodyne detection\index{Homodyne detection} (Sec.~\ref{sec:homodyne}), which performs a projection along an arbitrary axis in phase-space, allowing $\hat{x}$ and $\hat{p}$, or any linear combination of the two, to be directly sampled, i.e referring to Eq.~(\ref{eq:xp_theta}), we can access the observables $\hat{x}_\theta$ and $\hat{p}_\theta$ for any $\theta$.

Using a 50:50 beamsplitter to implement the reverse of Bell pair preparation, one can construct a Bell analyser for performing projections in the Bell basis\index{Bell measurements}, gifting us a highly-cherished entangling operation, useful for all manner of protocols (Part.~\ref{part:protocols}).

@@

The logical generalisation of the CZ gate is,
\begin{align}
\hat{U}_\mathrm{CZ} = e^{\frac{i}{2} \hat x_1 \hat x_2},
\end{align}
which transforms two-mode quadrature eigenstates as,
\begin{align}
\hat{U}_\mathrm{CZ} \ket{s}_1 \ket{t}_2 = e^{\frac{i}{2} s_1 t_2} \ket{s}_1\ket{t}_2.
\end{align}
Intuitively, it is evident upon inspection of the form of the generalised CZ gate that it leaves logical basis state amplitudes unchanged, but adds state-dependent phases to them. Qualitatively, this is exactly what a regular CZ gate does in the space of two qubits, except that the basis is discrete rather than continuous.

@@

\begin{figure}[!htbp]
	\begin{align}
		\Qcircuit @C=.7em @R=.4em @! {
		\lstick{\ket{\psi}} & \ctrl{1} & \qw & \meter & \hat{U}^\dag\hat{p}\hat{U} = m \\
		\lstick{\ket{0}_p} & \ctrl{0} & \gate{F} & \gate{X(m)} \cwx & \rstick{\hat{U}\ket\psi} \qw \\
		} \nonumber
	\end{align}
	\captionspacefig \caption{The single-mode teleporter using CV state encoding, structurally almost identical to an ordinary single-qubit teleporter, just substituting the operations with their respective CV generalisations. The circuit teleports the input state $\ket\psi$ from the first mode to the second mode, accumulating the action of the single-mode gate $\hat{U}$ applied to the first mode prior to measurement.} \label{fig:CV_teleporter}\index{Continuous variables!Teleporter}
\end{figure}

Having demonstrated an equivalent single-mode teleporter, we have all we need to construct arbitrary measurement-based quantum computations using the generalised CZ gates as the primitive entangling operation\index{Entangling operation} for preparation of the substrate graph state.

@@

Having demonstrated fault-tolerance, it can be concluded that CV optical quantum computation is viable, and scalable with efficient error correction resource overheads.
